Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-12 Chapters/Chap3/Numerics.tex
Add Figures
update figures

In each case the absolute vale is independent of $i,j$.  Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$. Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}. The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}. The field can change the sign of $J_1$ and $D_2$ for strong amplitudes. Finally, in Figure \ref{Fig3.2} we plot the SDW NN angle $\theta$ limited to the case $J_1 > 0$ and $D_2 > 0$.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Chapters/NNvsNNN.pdf}
  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
  \label{Fig3.1:NNvsNNN}
\end{subfigure}%
\hspace*{\fill}
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Chapters/ratio.pdf}
  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
  \label{Fig3.1:ratio}
\end{subfigure}
\label{Fig3.1}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.5\linewidth]{Chapters/theta.pdf}
  \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$. The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$.}
\label{Fig3.2}
\end{figure}

>>>>

In each case the absolute vale is independent of $i,j$.  Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$. Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}. The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}. The field can change the sign of $J_1$ and $D_2$ for strong amplitudes. Finally, in Figure \ref{Fig3.2} we plot the SDW NN angle $\theta$ limited to the case $J_1 > 0$ and $D_2 > 0$.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/NNvsNNN.pdf}
  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:NNvsNNN}
\end{subfigure}%
\hspace*{\fill}
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/ratio.pdf}
  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:ratio}
\end{subfigure}
\label{Fig3.1}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.5\linewidth]{Figures/theta.pdf}
  \caption{The spin wave density NN angle $\theta$ as a function of $\mathcal{E}$. The field modifies the ratio $\frac{J_{1}}{D_{2,ij}}$ thus modifying the wave vector. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
\label{Fig3.2}
\end{figure}

### 2019-02-12 Paper/paper.tex
update figures

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.
